---
title: 'Assignment 1: R Markdown practice'
author: "SoJeong Mun"
date: "`r Sys.Date()`"
output:
  pdf_document:
    dev: pdf
    df_print: kable
    fig_caption: no
    highlight: tango
    number_sections: yes
    toc: no
  word_document:
    toc: no
  html_document:
    dev: svg
    df_print: kable
    fig_caption: no
    number_sections: yes
    self_contained: yes
    smart: yes
    theme: paper
    toc: no
geometry: margin=1in
fontsize: 11pt
documentclass: article
urlcolor: blue
---

<!-- Write your Markdown below this line -->
# Section
Section CDS101-K02  

# Course Goals
By the end of the course, students will be able to:  

* Use GitHub For Creating a reproducible research document.  
-- My GitHub username is: _SoJeong Mun_  

* Obtain, clean, transform, and visualize a dataset using the R Programming language.  
* Interpret and predict dataset trends using statistical inference and models.  
* Critically examine and interpret Statistical claims reported in mass media.  

# Including Code  
## Running R code in a code chunk  

```{r}
x <- 2+2
x + 3
```
The output of first line of code is not printed out because it is assigned to a variable instead.  
The second line of output is printed out instead, but this means that the calculated value has not been saved for future use.  

## Displaying Graphs

```{r}
ggplot2::qplot(data = iris, x = Sepal.Length, y = Sepal.Width)
```
